\section{Discussion}
\label{sec:discussion}

\paragraph{The certificate is a conservative lower bound.}
The empirical coverage under the budget ($0.988$) sits well above the certified floor
($0.75$), and the construction explains the gap. Theorem~\ref{thm:composed} composes the
two miscoverage events through a union bound, which is tight only when the two failures
are disjoint. In practice the soft-sensor and prognostic failures are positively
correlated in the regimes that matter, because aggressive operation pushes the soft
sensor out of its calibration regime and loads the pump at the same time, so the two
modules tend to be stressed together. Positive failure correlation makes the true joint
coverage exceed the Bonferroni bound, and the deliberately conservative Lipschitz
constants ($L_1=L_2=0.15$ against a swept $L_1\approx0.024$) widen the gap further. The
certificate is therefore a guarantee, a floor that is provably met, rather than a
prediction of the coverage actually achieved. Tightening it is a concrete next step: a
joint failure-correlation model, built from a copula on the two nonconformity scores,
from multivariate conformal prediction, or from conformal risk control under dependence,
would replace the union bound with a dependence-aware composition and recover much of the
margin.

\paragraph{From per-cycle to the operating horizon.}
Theorem~\ref{thm:composed} is a per-cycle, marginal guarantee. A campaign runs over many
cycles, and a naive union of the per-cycle bound over a horizon of $K$ cycles degrades
linearly in $K$. The route to a genuine horizon guarantee is adaptive conformal
inference~\citep{gibbs2021}, which the soft-sensor module already
implements~\citep{busico_m1}. By adjusting the conformal quantile online it secures
long-run coverage under arbitrary, unspecified dependence, which is exactly the
dependence that feedback induces across cycles. Lifting the per-cycle certificate to a
horizon statement under this mechanism, in a dynamic rather than quasi-static setting, is
the principal direction of ongoing work, and it is what connects the present result to a
physically deployed implementation.

\paragraph{The selection term, and when it is not zero.}
The selection penalty $\Delta_{\mathrm{sel},k}$ vanishes here as a property of the loop
(Assumption~\ref{ass:causal}), not as an idealization, because the synchronous controller
forms each decision from the previous cycle's information and applies it before the
current measurement is realized. Carrying the term explicitly is worthwhile because it
identifies precisely when conformal validity would instead be lost, namely under a
non-causal co-selection in which the optimizer chooses the decision using the same
residual that the coverage check then evaluates. Most treatments of conformal prediction
in feedback either assume the difficulty away or abandon the guarantee. Naming the
selection effect, bounding it, and showing that it is null under realizable timing is what
makes the closed-loop certificate honest.

\paragraph{Scope and generality.}
The certificate is instantiated for binary-key distillation through a similitude
coordinate built from the relative volatility, the Gilliland reflux coordinate, and the
stripping factor. That coordinate is the unit-specific ingredient. The composition logic
itself, namely per-module conditional coverage, the causal-timing argument, the Bonferroni
composition, and the convex $\psi$-budget, is unit-agnostic. Extending the framework to
multicomponent separations or to other unit operations requires identifying the
appropriate dimensionless groups for those units, after which the same machinery applies.
A second refinement concerns the Lipschitz constants, estimated here a~priori from a
regime sweep; an online estimator that re-identifies them as the plant ages would let the
budget adapt, and it pairs naturally with the adaptive-conformal horizon extension above.
The budget radius $\varepsilon$ is, finally, an explicit economic dial. It trades the
certified coverage level directly against the profit the optimizer is permitted to chase,
and exposing that trade-off quantitatively is one of the practical contributions of the
framework.
