\section{Conclusion}
\label{sec:conclusion}

Soft sensing, prognostics, and real-time optimization each ship a calibrated uncertainty
guarantee, but a closed-loop operator needs a guarantee on the joint system-safety event,
namely an in-specification product together with surviving equipment, and that joint
guarantee does not follow from the three taken separately. This paper supplied it. The
per-cycle composed coverage certificate of Theorem~\ref{thm:composed} states the joint
guarantee explicitly, with terms that map one-to-one onto the three modules, and a
causal-timing argument shows that feedback does not void it: the conformal-selection
penalty is exactly zero whenever the decision is formed before the measurement it is
conditioned against. Corollary~\ref{cor:floor} then converts the certificate into a
single convex $\psi$-budget that a modifier-adaptation optimizer enforces directly, so
that the flagship guarantee and the operating floor are one and the same constraint, and
the optimizer is barred from pushing economics hard enough to invalidate its own sensor
and life guarantees.

On a calibrated debutanizer twin running the real soft-sensor, prognostic, and
optimization implementations, the certified floor $1-(\alpha_1+\alpha_2)-\varepsilon =
0.75$ was met empirically, with joint safety coverage of $0.988$ under the budget and
$0.000$ without it, the entire contrast carried by reflux-pump life. None of the three
guarantees implies system safety on its own; the composition is the certificate.

Three directions follow. The per-cycle certificate should be lifted to a horizon
guarantee under adaptive conformal inference and realized on a dynamic high-fidelity
simulator and on plant data, moving from the quasi-static demonstration given here to a
physically deployed loop. The Bonferroni composition should be tightened with a
dependence-aware model of the joint soft-sensor and prognostic failure, which would
recover the margin that positive failure correlation currently leaves unused. Finally,
the framework should be carried from a single column to a plant, with the coverage budget
allocated across units. That last step is what turns a certificate for one column into a
certificate for an integrated process.
