A self-optimizing plant is safe only when a joint event holds: the product stays in
specification while the equipment survives to its next maintenance window. We show that this
joint guarantee can be certified in closed loop, that feedback does not void it, and that a
single convex constraint forces a profit-seeking optimizer to respect it. Soft sensors,
prognostic models, and real-time optimization (RTO) each now ship distribution-free coverage
guarantees, yet the joint event that determines safety follows from none of them in
isolation, and feedback is widely believed to break the exchangeability on which conformal
validity rests. We derive a per-cycle \emph{composed} coverage certificate for the joint
event, with terms that map one-to-one onto the three modules: the soft sensor's miscoverage,
the prognostic bound's miscoverage, a similitude-departure penalty contributed by each
module's regime shift, and a selection penalty. A causal-timing argument then shows that the
selection penalty is exactly zero whenever the decision is formed before the measurement it
is conditioned against, which dissolves the feedback objection. A corollary collapses the
certificate into a single convex similitude-departure budget that a modifier-adaptation RTO
enforces directly, so the optimizer cannot push economics hard enough to invalidate its own
sensor and life guarantees, and the flagship guarantee and the operating floor become the
same constraint. A negative control isolates the mechanism. On a calibrated debutanizer
digital twin running the real soft-sensor, prognostic, and RTO implementations, the certified
floor $1-(\alpha_1+\alpha_2)-\varepsilon = 0.75$ is met empirically, with joint safety
coverage $0.988$ ($95\%$ interval $[0.976, 0.994]$) when the budget is enforced; removing the
budget, the single causal ingredient, collapses joint coverage to $0.000$. Reflux-pump life
carries the entire contrast, with remaining-life coverage of $1.000$ against $0.013$. None of
the three guarantees implies system safety on its own; the composition, and the convex budget
that enforces it, is what the certificate provides.
