\documentclass[review,times]{elsarticle}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{lineno}
\linenumbers

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\theoremstyle{remark}
\newtheorem{remark}{Remark}
\DeclareMathOperator{\dtv}{d_{\mathrm{TV}}}
\newcommand{\law}[1]{\mathcal{V}_{#1}}
\newcommand{\lawt}[1]{\tilde{\mathcal{V}}_{#1}}
\journal{Reliability Engineering \& System Safety}

\begin{document}
\begin{frontmatter}
\title{Similarity-Calibrated Conformal prediction: data-free coverage guarantees for
remaining-useful-life intervals under operating-regime transfer}
\author{Bien Busico}
\address{Map\'ua Malayan College Mindanao, Davao City, Philippines}

\begin{abstract}
Prognostics supports condition-based maintenance and safety decisions, where a remaining-useful-life
(RUL) interval is only as good as its stated confidence. Conformal prediction gives a
distribution-free coverage guarantee for such models, but only under exchangeability, which fails
when a model calibrated on assets in one operating regime is deployed on assets in another: the
interval then miscovers with no warning. The two standard fixes do not suit reliability practice:
reweighting methods need target failure data a new asset lacks, and dimensionless transfer learning
improves point accuracy but carries no coverage guarantee. We present Similarity-Calibrated Conformal
(SCC) prediction, a deployable method that calibrates the conformal quantile in a physics-derived
dimensionless coordinate (via the Buckingham $\Pi$ theorem) so that coverage transfers across
operating regimes with no target failure data. SCC adds two features a practitioner can act on: an
a-priori coverage bound computable from physical parameters alone, the cross-regime shortfall being
at most $2L\lVert\Delta\boldsymbol\psi\rVert$ in a similitude-departure quantity, and a runtime
diagnostic returning holds, violated, or indeterminate so the method declines to certify rather than
miscover. On a controlled catalyst-deactivation reliability testbed, regime-blind conformal miscovers
(coverage falls to 0.58) while SCC recovers it to within 0.006 of target; under a controlled
departure the coverage gap and interval back-off degrade gracefully and monotonically, and the
a-priori bound holds on 100\% of held-out configurations. On the FEMTO bearing benchmark the
diagnostic correctly places that dataset outside the method's envelope. Validation on adequately
powered field data is the next step.
\end{abstract}

\begin{keyword}
conformal prediction \sep uncertainty quantification \sep remaining useful life \sep
dimensional analysis \sep transfer learning \sep prognostics
\end{keyword}
\end{frontmatter}

\input{sections/01_introduction}
\input{sections/02_background}
\input{sections/03_method}
\input{sections/04_experimental_design}
\input{sections/05_results}
\input{sections/06_discussion}
\input{sections/07_conclusions}

\section*{Data and code availability}
The SCC implementation, the deactivation testbed, the diagnostic, and scripts reproducing every
figure and table are available at \texttt{github.com/beebzy-droid/IPIS}.

\section*{CRediT authorship contribution statement}
\textbf{Bien Busico:} Conceptualization, Methodology, Software, Formal analysis, Validation,
Writing -- original draft.

\section*{Declaration of generative AI use}
During preparation the author used a generative AI assistant for derivation checking, code
scaffolding, and editing. The author reviewed and verified all content and takes full
responsibility for it.


\appendix
\input{sections/08_appendix}

\bibliographystyle{elsarticle-num-names}
\bibliography{scc_refs}
\end{document}
