\section{Case-study design}
\label{sec:case}

\subsection{Plant evaluations: the feed-composition campaign}

The twin of Section~\ref{sec:methods-twin} is exercised over a grid in the decision and
disturbance variables to produce the plant evaluations all results rest on. The campaign
spans feed light-key fractions $z\in\{0.30,0.325,0.35,0.375,0.40\}$ crossed with reflux
ratios and distillate flows covering the decision box, each case solved to convergence in
DWSIM and screened for mass-balance closure and solver staleness. The accepted set is $77$
operating points. A nominal sub-sweep at $z_0=0.35$ supplies the $15$ points that fit the
optimiser's nominal surfaces $\hat g$, distillate purity, and reboiler duty, while the full
$77$-point set fits the truth surface $g(u,z)$.

Two facts about the campaign shape the design. First, the bottoms composition responds
strongly and monotonically to feed composition: at a fixed mid-box setpoint $x_B$ rises by an
order of magnitude across the sampled $z$ range, which confirms that the disturbance genuinely
propagates to the constrained quantity and that the monotone-$z$ oracle of
Section~\ref{sec:methods-rto} is well founded. Second, the specification is physically
unattainable for large feed excursions. For $z\gtrsim0.38$ the minimum achievable $x_B$ within
the distillate-flow bounds exceeds the spec; at $z=0.40$ the column floor is $x_B\approx0.048$,
well above $\bar g=0.02$, because removing enough light key to meet spec would require a
distillate flow outside the operable range. The whole $[0.30,0.40]$ ensemble is therefore
infeasible for any back-off, which is itself the rationale for a tightly controlled feed: the
operational disturbance must be small, consistent with the realistic $\sigma_z\approx0.006$
anchor used below.

\subsection{Disturbance sweep and calibration}

The disturbance magnitude is swept over
\[
\sigma_z\in\{0.004,\,0.006,\,0.008,\,0.010,\,0.015,\,0.020,\,0.025\},
\]
with $\sigma_z=0.006$ taken as the
operationally realistic centre (a well-controlled upstream feed) and the larger values probing
how each method degrades as the feed becomes more variable. For each $\sigma_z$ the calibration
set of Section~\ref{sec:methods-backoffs} is drawn with size scaled to the disturbance,
$n=\lfloor 1500\cdot\max(1,\sigma_z/0.006)\rfloor$, reflecting that the conditional-quantile
estimate needs more data as the disturbance widens; at the realistic centre $n=1500$. All
draws use a fixed seed so the regime map reproduces exactly on a given platform.

\subsection{Methods compared}

Four back-off constructions enter the comparison. The oracle (the true conditional quantile,
Section~\ref{sec:methods-rto}) is the achievable benchmark. The constant margin
($C_{\mathrm{fix}}$) and the normalised, adaptive back-off ($C_{\mathrm{nrm}}$) are the two
marginally valid baselines, the latter being the soft-sensor-style interval our earlier
design used. The conditional method, CQR with a-posteriori calibration ($C_{\mathrm{cqr}}$
followed by the $\kappa$-step of Section~\ref{sec:methods-apost}), is the proposed remedy.
Each method produces a back-off field over the decision box; the RTO of
Eq.~\eqref{eq:backoff} selects the profit-maximising feasible setpoint; and that setpoint is
then scored against the truth surface.

\subsection{Metrics and protocol}

The primary metric is the realised constraint-violation rate at the selected setpoint, $\hat
v(u^\star)=\widehat{\mathbb P}_z[g(u^\star,z)>\bar g]$, estimated by Monte-Carlo over the
disturbance with $4$ to $6\times10^{3}$ draws; the target is $\hat v\le\alpha=0.10$. The
secondary metric is the operating profit $\pi(u^\star)$, reported only to show that calibrated
safety is not bought at a cost in profit, never as a performance claim in its own right,
because at realistic disturbance the constraint is barely active and all methods sit within a
fraction of a percent of the deterministic optimum. Feasibility is itself an outcome: a method
is reported infeasible at a given $\sigma_z$ when no back-off, after a-posteriori inflation
where applicable, admits a setpoint meeting the target. The a-posteriori inflation factor
$\kappa^\star$ is logged as a diagnostic of data adequacy.

Because the realised violation is a Monte-Carlo quantity, the reported rates carry sampling
noise of order $\pm0.01$ to $0.02$ across platforms even though they are seeded within a
platform; the regime structure and the magnitude of the selection effect are stable to this
noise. The truth surface itself is validated by a leave-one-feed-composition-slice-out test,
fitting on all $z\neq0.375$ and predicting the held-out $z=0.375$ slice, which bounds the
accuracy of every violation estimate (Section~\ref{sec:results-valid}). The specification is
$\bar g=0.02$, the miss level $\alpha=0.10$, the decision box $[0.8,3.0]\times[33,37]$, and the
master seed $20260614$ throughout.
