\section{Discussion}
\label{sec:discussion}

\subsection{The general lesson: conformal-in-the-loop needs conditional validity}

The result is narrow in its case study but general in its mechanism. Nothing in the
selection-effect argument of Section~\ref{sec:methods-selection} is specific to a debutaniser or
to feed composition. It follows from two facts that hold whenever a conformal interval is placed
inside an optimisation. First, split and locally adaptive conformal prediction guarantee
coverage marginally, averaged over the calibration distribution, and the conditional coverage
varies across the input space. Second, an optimiser is a selection operator that seeks the
boundary of the feasible region and therefore lands preferentially where the margin is tightest
relative to the local risk, which is where coverage is worst. Any pipeline with these two
features, a marginally calibrated margin and an optimiser pressing on it, will show the same
degradation. This includes back-offs in stochastic and learning-based model-predictive control,
constraint handling in safe Bayesian optimisation, and any chance-constrained program that sizes
its margin from a marginally valid predictor. The practical implication is a design rule: a
conformal margin used as a hard optimisation constraint must be conditionally valid at the
operating point, not merely marginally valid over a calibration set. Where conditional validity
cannot be guaranteed in advance, an a-posteriori calibration at the selected solution
\citep{zhao2024cpp} is necessary, but, as Section~\ref{sec:results-boundary} shows, that step is
small and reliable only when the base margin is already conditional. On a marginal base it must
inflate the margin severalfold, and it can fail outright.

\subsection{What the method does and does not buy}

The contribution is calibrated violation control, and the honest accounting of its value has two
parts. On safety, the conditional method delivers what the marginal baselines cannot, a realised
violation that tracks the oracle to within the Monte-Carlo band across the operationally
realistic disturbance range, where the naive-adaptive margin violates roughly five times the
nominal rate and the fixed margin is either over-violating or infeasible. On profit, the method
buys essentially nothing at the realistic operating point, where every method, including the
deterministic optimum, lies within half a percent, because at a well-controlled feed the chance
constraint is barely active. We regard the second fact as a feature of the honest framing rather
than a weakness. The value of a safety margin is not that it raises profit but that it removes a
violation the unsafe alternative incurs while appearing to be slightly more profitable. The
profit separation widens only as the disturbance grows and the constraint begins to bind, by
which point the marginal methods have already failed. A reader looking for a profit headline will
not find one here, and should not, because the result is about constraint integrity under
uncertainty.

\subsection{Limitations}

Several boundaries should be read with the result. The plant is a simulation twin, a rigorous
DWSIM Peng--Robinson model validated by leave-one-disturbance-out interpolation ($R^2=0.917$, MAE
$0.0053$ in $x_B$), but it is not plant data; the selection-effect mechanism is structural and
should transfer, yet the specific magnitudes, the fivefold factor and the regime boundaries, are
twin-specific. The study uses a single binary n-butane and n-hexane system, one unmeasured
disturbance (feed composition), and a two-dimensional decision. A higher-dimensional decision or
several simultaneous disturbances would enlarge the space over which the conditional quantile must
be estimated, and would therefore bring the data-starvation boundary of
Section~\ref{sec:results-boundary} to smaller disturbance magnitudes than observed here. The
reported violation rates are Monte-Carlo estimates carrying a band of $\pm0.01$ to $0.02$, and the
truth-surface error, about $0.005$ in $x_B$, is a precision floor below which no violation
difference can be resolved; the qualitative claims sit far outside that band, but fine rankings
near the target should not be over-read. The oracle is a benchmark, not a method, because it uses
the true plant response and the monotone-in-$z$ structure to evaluate the conditional quantile in
one shot; the conformal methods make no monotonicity assumption, but a non-monotone or multi-modal
constraint response would require the oracle itself to be estimated rather than read off, which
complicates only the benchmark and not the proposed method. Finally, the a-posteriori step
requires an independent calibration draw at the selected setpoint; in deployment this is a
held-out window of operating data, and its size sets how tightly the residual gap can be closed.

\subsection{Toward closed-loop and plant deployment}

This paper is the static, open-loop foundation, in which the disturbance is unmeasured and the
optimiser commits to a setpoint under a calibrated margin. The natural extension is closed-loop,
where an online estimate of the constrained quantity, supplied by the soft sensor of the companion
paper that infers the unmeasured composition from tray temperatures, feeds back so that the
back-off contracts as the disturbance becomes partially observed and the operating point tracks
it. That closed-loop study, with the sensor in the loop and the disturbance evolving in time, is
left to future work, and the exchangeability questions it raises, calibration under feedback and
temporal dependence, connect directly to the beyond-exchangeability conformal literature of
Section~\ref{sec:related}. The other clear next steps are validation on plant or pilot data, where
the disturbance law is empirical rather than assumed, and extension to multi-component products
and higher-dimensional decisions, where the cost of conditional estimation is the binding
constraint. In all of these, the design rule above is the portable result: size the margin
conditionally, and read the a-posteriori inflation as the signal that the data can no longer
certify the target.
