\section{Conclusion}
\label{sec:conclusion}

Real-time optimisation must subtract a back-off from a quality specification to protect a
constraint it cannot measure, and conformal prediction is the natural distribution-free way to
size that back-off. We have shown that the natural choice is unsafe. An optimiser pressing on a
marginally valid conformal margin, even a locally adaptive one, behaves as a selection mechanism
that drives the operating point to where the margin under-covers the conditional constraint
quantile, so the realised violation reaches roughly five times the nominal level across the
disturbance range. An oracle margin built from the true conditional quantile holds the violation
at the target, which confirms that the failure is in the back-off, not in the chance-constrained
formulation. The remedy is conditional validity. A conformalised-quantile-regression back-off,
with an a-posteriori calibration step at the selected setpoint, returns the realised violation to
the oracle level at near-oracle profit over the operationally realistic disturbance range, and it
degrades only, and diagnosably through a climbing inflation factor, when the disturbance widens
beyond several times the realistic level and the conditional estimate runs out of calibration
data. A regime map over disturbance magnitude characterises where each margin controls violation,
where a constant margin becomes infeasible, and where even the conditional method can no longer
certify the target.

The contribution is calibrated safety, not profit. At a well-controlled feed the constraint is
barely active and all methods earn within half a percent of the deterministic optimum, so the
value of the conditional method is the violation it removes, not the profit it adds. The mechanism
is general, since any conformal interval used as a hard optimisation constraint is exposed to the
same selection effect, and the portable design rule is to size the margin conditionally and to
read the a-posteriori inflation as a signal of data adequacy. Demonstrated here on a rigorous
binary-distillation twin, the approach sets up a closed-loop extension in which an online soft
sensor of the unmeasured quality feeds the back-off as the disturbance is partially observed.
