\section{Introduction}
\label{sec:intro}

Closed-loop process operation is judged over a campaign, not a single cycle. What matters
operationally is the long-run frequency with which the plant simultaneously meets its product
specification and preserves its equipment to the next planned maintenance window. This paper
gives a distribution-free guarantee on exactly that horizon-wide joint event for a closed loop
with realistic dynamics and delayed measurements, and shows that it holds where the obvious
construction does not.

A per-cycle version of the guarantee already exists. The composed coverage certificate of
\citet{busico_m4} bounds the one-cycle joint event, the product staying in specification and
the equipment surviving, under exchangeable calibration residuals, by summing a soft-sensor
budget \citep{busico_m1}, a prognostic budget \citep{busico_m2}, and the conditional-calibration
budget of a conformal real-time optimiser \citep{busico_m3}. Two things break when the loop is
actually run. Feedback makes successive cycles dependent, so exchangeability fails; and
laboratory or analyser labels return several cycles late, so the residuals that calibrate the
bound are stale. The natural repair, a Bonferroni union bound that charges each cycle a fraction
of the error budget to cover $K$ cycles jointly, becomes vacuous as $K$ grows. A horizon
guarantee therefore needs a different mechanism, not a tighter bookkeeping of the per-cycle one.

We supply that mechanism by lifting the per-cycle certificate with adaptive conformal inference
\citep{gibbs2021}, and we realise the loop dynamically so the claim is tested against transport
lags and analyser dead time rather than asserted on a quasi-static surrogate. The contributions
are four.
\begin{enumerate}
\item \textbf{R1, a deployable horizon-wide safety certificate.} Adaptive calibration carries the
  per-cycle floor to the campaign: the conformal health-constrained loop holds the joint safety
  event at its certified floor over the horizon, with a $95\%$ Wilson lower bound of $0.992$
  against a floor of $0.75$.
\item \textbf{R2, the certificate's operational value, quantified.} A health-blind optimiser
  meets the quality specification on essentially every cycle yet over-refluxes until projected
  remaining useful life collapses, dropping the joint event to $0.008$, while the constrained
  loop holds it. Meeting a specification is not the same as operating safely, and the health
  channel with its budget is what closes the gap.
\item \textbf{R3, validity that is invariant to measurement dead time.} The conformal selection
  penalty stays zero under arbitrary label delay, so dead time moves into the coverage rate
  rather than breaking validity; the joint coverage stays at $1.000$ across delays of zero to
  eight cycles.
\item \textbf{R4, evidence that adaptivity is necessary.} Adaptive calibration keeps a finite
  interval at target coverage across horizons at which the naive union bound is already vacuous.
\end{enumerate}

This paper completes the IPIS series, which develops a physics-anchored soft sensor
\citep{busico_m1}, a similarity-calibrated prognostic certificate \citep{busico_m2}, a
conditionally calibrated conformal real-time optimiser \citep{busico_m3}, and the per-cycle
composed certificate \citep{busico_m4} that the present work lifts to a horizon.
Section~\ref{sec:framework} develops the framework: the per-cycle certificate, its dynamic
realisation, the delayed-label read-off, the dead-time argument, and the horizon guarantee. The
case study fixes the debutanizer twin and the two control arms, and Section~\ref{sec:results}
reports the campaign behaviour against the three results above. The discussion places the
guarantee as a runtime safety monitor and the bridge to plantwide risk allocation.
