\section{Related work}
\label{sec:related}

Conformal prediction supplies finite-sample, distribution-free coverage under exchangeability
\citep{vovk2005, shafer2008}. Split and inductive variants make it cheap enough for online
regression \citep{lei2018, angelopoulos2023}, and conformalized quantile regression adapts the
interval width to local difficulty \citep{romano2019}. These deliver per-instance marginal
coverage, which is exactly the ingredient the per-cycle composed certificate of
\citet{busico_m4} sums across its soft-sensor and prognostic channels.

Closed-loop data are not exchangeable, because feedback couples successive cycles. Two lines of
work extend conformal validity past exchangeability. Reweighting recovers coverage under a
covariate shift that is known or estimable \citep{tibshirani2019}, and the
beyond-exchangeability framework bounds the coverage gap by a total-variation-type term for
general dependent data \citep{barber2023}. These results justify that a conformal interval need
not collapse when a control loop introduces dependence, but they do not on their own deliver a
long-run guarantee over a horizon under a feedback policy.

Adaptive conformal inference closes that loop directly. It treats the miscoverage level as a
state updated online from realised errors and guarantees a long-run coverage frequency however
the distribution drifts \citep{gibbs2021}. This long-run, shift-robust property is the engine of
the horizon guarantee developed here, and, as Section~\ref{sec:o1} shows, it tolerates the
delayed feedback that analyser dead time imposes.

On the control side, real-time optimisation drives a plant toward its economic optimum despite
plant-model mismatch, classically through modifier adaptation
\citep{marchetti2009, chachuat2009}, while self-optimizing and plantwide control frame which
variables to hold so that economic loss stays bounded \citep{skogestad2000}. The IPIS optimiser
\citep{busico_m3} adds a conformal back-off so that the economic push respects a chance
constraint; the present work asks what that back-off guarantees over a whole campaign rather
than at a single cycle.

This paper is the realisation layer of the IPIS series, which develops a physics-anchored soft
sensor \citep{busico_m1}, a similarity-calibrated prognostic certificate \citep{busico_m2}, the
conformal real-time optimiser \citep{busico_m3}, and the per-cycle composed certificate
\citep{busico_m4}. To our knowledge none of this prior work delivers a horizon-wide guarantee on
a joint quality-and-equipment-health event in a dynamic closed loop with delayed labels.
Establishing that guarantee, and showing that the naive union-bound alternative is vacuous at
realistic horizons, is the gap this paper fills.
