\section{Framework}
\label{sec:framework}

\subsection{The per-cycle composed certificate}
\label{sec:percycle}

Each decision cycle $k$ produces a setpoint $u_k=(R_k,D_k)$, the reflux ratio and the
distillate rate. Under that setpoint the column realises a bottoms impurity $x_k$ and the
reflux pump carries a projected remaining useful life $\rho_k$. The operating requirement is
the \emph{joint} safety event
\begin{equation}
  S_k \;=\; \{\, x_k \le x_{\mathrm{spec}} \,\}\;\cap\;\{\, \rho_k \ge \rho_{\min} \,\},
  \label{eq:Sk}
\end{equation}
the product staying in specification \emph{and} the equipment surviving to its next planned
maintenance window. The composed coverage certificate of \citet{busico_m4} guarantees this
event one cycle at a time: under exchangeable calibration residuals and a similarity budget
$\varepsilon$,
\begin{equation}
  \Pr(S_k) \;\ge\; 1-(\alpha_1+\alpha_2)-\varepsilon,
  \label{eq:floor}
\end{equation}
where $\alpha_1$ is the soft-sensor miscoverage \citep{busico_m1}, $\alpha_2$ the prognostic
miscoverage \citep{busico_m2}, and $\varepsilon$ the conditional-calibration budget that the
conformal back-off of the real-time optimiser spends \citep{busico_m3}. We call the
right-hand side of \eqref{eq:floor} the certified floor. The bound is per cycle and rests on
exchangeability. The aim of this paper is to make it hold across an operating \emph{horizon}
once the loop is closed, so that successive cycles are dependent and the labels that calibrate
the bound arrive late.

\subsection{Dynamic realisation}
\label{sec:dynamic}

The certificate is established on a quasi-static twin, in which a setpoint maps instantly to
its steady-state outcome. A real column does not. We therefore retain the validated
steady-state response surface $g(\cdot)$ of the twin \citep{busico_m3}, fitted from the
process simulator, as a nonlinear static gain, and wrap it in linear transport dynamics. The
result is a Hammerstein-class plant with three transport elements, each a measured or
specified time constant rather than a free parameter:
\begin{enumerate}
\item an actuator first-order lag, so the realised setpoint $(\tilde R_k,\tilde D_k)$ relaxes
  toward the commanded $(R_k,D_k)$ with time constant $\tau_{\mathrm{act}}$;
\item a process first-order lag, so the impurity and the sensor temperature relax toward their
  steady-state targets $g(\tilde R_k,\tilde D_k)$ with constants $\tau_{\mathrm{proc}}$ and
  $\tau_{\mathrm{temp}}$;
\item an analyser dead time $\theta_a$ on the measured impurity, reflecting the
  gas-chromatograph cycle.
\end{enumerate}
By construction the settled steady state reproduces the twin exactly, so the calibration that
underlies \eqref{eq:floor} transfers without re-estimation. The loop runs on two timescales: a
fast integration step $\Delta t$ for the dynamics, and a slower decision interval
$T_{\mathrm{rto}}=n_{\mathrm{sub}}\,\Delta t$ at which a new setpoint is computed and then held.
Holding $u_k$ across the interval, rather than applying it instantaneously, is what makes the
similarity coordinate evolve along the realised path and what exposes the certificate to the
plant dynamics it must now survive.

\subsection{Delayed labels and the adaptive read-off}
\label{sec:adaptive}

A laboratory or analyser measurement of cycle $k$ does not return until $D_a$ decision cycles
later, where $D_a=\lceil \theta_{\mathrm{lab}}/T_{\mathrm{rto}}\rceil$. The horizon read-off
therefore replaces the per-cycle conformal quantile with an adaptive one
\citep{gibbs2021}. Writing $s_j$ for the soft-sensor nonconformity score of cycle $j$ and
$\mathrm{err}_j=\mathbf{1}[\,s_j>\hat q_j\,]$ for its miscoverage indicator, the adaptive level
follows
\begin{equation}
  \alpha_{t+1} \;=\; \alpha_t + \gamma\,\big(\alpha_1 - \mathrm{err}_{t}\big),
  \label{eq:aci}
\end{equation}
and the interval that the optimiser backs off against at cycle $k$ is
$\mathcal{C}_k=\hat y_k \pm \hat q\big(1-\alpha^{(k)}\big)$. Because the label for cycle $j$
is only consumed at cycle $j+D_a$, the level $\alpha^{(k)}$ that forms $\mathcal{C}_k$ depends
only on scores
\begin{equation}
  \{\, s_j : j \le k-1-D_a \,\},
  \label{eq:usable}
\end{equation}
that is, on residuals that are stale by $D_a$ cycles relative to the no-delay case. This is the
standard delayed-feedback regime for adaptive conformal inference, and it is the only channel
through which dead time enters the guarantee.

\subsection{Validity under dead time}
\label{sec:o1}

A closed loop raises a selection concern: if the optimiser were to choose $u_k$ using the same
sample later used to check coverage at cycle $k$, the marginal guarantee would no longer hold,
and \citet{busico_m4} carry an explicit selection penalty $\Delta_{\mathrm{sel},k}$ that is
non-zero only in that configuration. Dead time does not create such co-selection. By
\eqref{eq:usable} the interval $\mathcal{C}_k$ is a function of scores no newer than
$k-1-D_a$, and for every $D_a\ge 0$ this set excludes $s_k$ itself, since $k>k-1-D_a$. The
cycle-$k$ interval is thus formed without reference to the cycle-$k$ outcome it is scored
against, so the per-cycle result $\Delta_{\mathrm{sel},k}=0$ of \citet{busico_m4} is preserved
under arbitrary label delay. What dead time does change is that $\alpha^{(k)}$ is built from
older residuals; its effect is a transient in the coverage \emph{rate}, of order $D_a/K$ over a
$K$-cycle horizon, which washes out as the horizon grows, and not a loss of validity. The
detailed timing argument is recorded in the supplementary note.

\subsection{The horizon guarantee}
\label{sec:horizon}

Equations \eqref{eq:aci}--\eqref{eq:usable} deliver a long-run coverage property for the
soft-sensor interval that is distribution-free and holds under the dependence that feedback
induces \citep{gibbs2021}: the realised miscoverage frequency converges to $\alpha_1$ up to an
$O(1/(\gamma K))$ term, with an additional $O(D_a/K)$ boundary term under delay. Composing this
long-run quality guarantee with the prognostic and budget terms of \eqref{eq:floor} carries the
per-cycle floor to the horizon: the campaign frequency of the joint event $S_k$ meets the
certified floor of \eqref{eq:floor}. The naive alternative, a Bonferroni union bound that
charges each cycle the level $\alpha_1/K$ to cover $K$ cycles jointly, requires the
$1-\alpha_1/K$ residual quantile per cycle; as $K$ grows this level exceeds what any finite
calibration set can resolve and the interval becomes vacuous, so static union bounds cannot buy
horizon coverage. Section~\ref{sec:results} reports both behaviours.
