\section{Case study}
\label{sec:case}

\subsection{Process twin}
The benchmark is a debutanizer column built in DWSIM \citep{dwsim} under the Peng-Robinson
equation of state \citep{peng1976}. From this twin we take the validated steady-state response
surface relating reflux ratio and distillate rate to the bottoms butane impurity
\citep{busico_m3} and use it as the nonlinear static gain of the dynamic plant; column
diagnostics follow standard correlations \citep{perrys}. Because the gain is the same surface
the per-cycle certificate was calibrated against, the settled steady state reproduces the twin
and the calibration transfers without re-estimation.

\subsection{Dynamic plant and health channel}
The static gain is wrapped in the transport dynamics of Section~\ref{sec:dynamic}. Representative
time constants are an actuator lag of about one minute on the manipulated setpoints, a
composition lag of about thirty minutes and a sensor-temperature lag of about fifteen minutes on
the outputs, and an analyser dead time of about five minutes on the measured impurity; the loop
is integrated at a one-minute step and a new setpoint is computed and held every sixty steps,
that is, every hour. The reflux pump degrades under an affinity cube law in the realised reflux,
and its projected remaining useful life is the equipment-health channel the certificate must
protect. These time constants are illustrative values, to be pinned per column from step-test
data; the coverage claim does not depend on them.

\subsection{Control arms}
Two arms share everything except a single switch. The health-blind arm lets the optimiser pull
reflux for economic benefit with no health constraint; the health-constrained arm caps that pull
with the conformal $\psi$-budget. The cap, not the conformal level, is what distinguishes the
arms, and both are scored against the same certified floor, so the contrast isolates the value of
enforcing the health budget.

\subsection{Configuration and reproducibility}
The frozen configuration is a bottoms-impurity specification of $0.02$, a minimum projected life
of $200$~h, soft-sensor and prognostic miscoverage $\alpha_1=\alpha_2=0.10$, and a similarity
budget $\varepsilon=0.05$, which set a certified floor of $0.75$. The two-arm contrast runs four
seeds over $120$ cycles; the delay and adaptivity sweeps run $400$ cycles, with a label delay of
two decision cycles unless that delay is itself swept. Every figure and number regenerates from a
single fixed seed through one script, and the headline numbers are frozen as committed evidence.
