\section{Discussion}
\label{sec:discussion}

Under adaptive calibration the per-cycle certificate of \citet{busico_m4} becomes a guarantee
that holds over the operating horizon rather than at an instant. In practice this turns the
certificate into a runtime monitor: at any point in a campaign the loop can state a
distribution-free lower bound on the frequency with which it has met the joint safety event,
and that bound does not weaken as the campaign lengthens (R1, Section~\ref{sec:horizon}).

The two-arm contrast in Figure~\ref{fig:two_arm} makes the operational content concrete, and it
is the result most likely to matter on a plant. A health-blind optimiser is in specification on
essentially every cycle and would pass any quality-only audit, yet it over-refluxes until
projected life collapses and the joint safety event falls to $0.008$, while the conformal
health-constrained loop holds the event at its floor. A quality specification and a safety
guarantee are different objects, and the binding $\psi$-budget is the mechanism that converts a
per-cycle bound into one sustained across the horizon (R2). The gap here is not subtle: it is
$0.008$ against $1.000$ on the same floor.

Delayed feedback is the feature of a real analyser loop most often assumed fatal to a conformal
guarantee, and it is not. Because the interval at a cycle never references that cycle's own
outcome, the selection penalty stays zero under any label delay (Section~\ref{sec:o1}), so
coverage remains valid; the only cost is a transient in the coverage rate, of order $D_a/K$,
which Figure~\ref{fig:deadtime} shows is small over the horizons tested (R3). It is worth
separating the property that survives dead time, validity, from the one that merely degrades
gracefully with it, the rate.

The contrast with the union bound in Figure~\ref{fig:gamma_union} is the methodological point. A
static Bonferroni allocation cannot buy horizon coverage without charging each cycle a vanishing
error level, at which point no finite calibration set resolves the required quantile and the
interval is vacuous; adaptive inference sidesteps this by spending a fixed long-run budget
rather than a per-cycle one \citep{gibbs2021}. Adaptivity is therefore not a refinement but a
requirement at realistic horizons (R4).

Several limitations bound these claims. The plant is a reduced-order Hammerstein realisation, a
validated static gain wrapped in transport lags rather than a tray-resolved dynamic column, so
the transient shapes are representative rather than exact and the time constants are
illustrative values to be pinned per column from step-test data. The coverage claim is itself
fidelity-agnostic: validity follows from the calibration construction, not from the plant's
internal accuracy, so what a higher-fidelity dynamic simulation would sharpen is the realism of
the coverage-rate transient, not the validity. A confirmation on a DWSIM dynamic column is the
natural next step. Finally, the deadtime transient is small here because the loop is
well-behaved; a deliberate drift or disturbance stress test would make the rate cost visible and
is left to future work.

The same composition that carries one column's certificate across a horizon points to the larger
target: allocating the similarity budget $\varepsilon$ across several units, so that a plantwide
certificate is assembled from per-unit ones under a shared risk allocation. That modular
extension, from one column to a plant, is the highest-leverage direction this framework opens.
