Process safety is judged over a campaign: what matters is the long-run frequency with which a
plant simultaneously meets its product specification and preserves its equipment to the next
maintenance window. We give a distribution-free guarantee on this horizon-wide joint event for a
closed loop with realistic dynamics and delayed measurements. A per-cycle version exists,
composing a soft-sensor budget, a prognostic budget, and the conditional-calibration budget of a
conformal real-time optimiser, but it assumes exchangeability and holds one cycle at a time.
Closed-loop feedback makes cycles dependent, laboratory labels arrive late, and the naive union
bound that would cover a horizon is vacuous. We realise the loop dynamically, as a validated
static gain wrapped in actuator, process, and analyser-deadtime transport lags, and lift the
per-cycle certificate with adaptive conformal inference. The conformal selection penalty is zero
under arbitrary label delay, so validity is preserved and dead time enters only the coverage
rate. On a debutanizer twin the health-constrained loop holds the joint event at its certified
floor of $0.75$ with a $95\%$ Wilson lower bound of $0.992$, whereas a health-blind optimiser
stays in specification on essentially every cycle yet over-refluxes until projected life
collapses, dropping the event to $0.008$. Coverage is invariant to label delays of zero to eight
cycles, and adaptive calibration keeps a finite interval at target coverage where the union
bound is vacuous beyond fifty cycles. The per-cycle certificate thus becomes a runtime,
horizon-wide safety monitor.
