\section{Background and related work}\label{sec:background}
\emph{Split conformal prediction} gives the guarantee SCC builds on. Given a nonconformity score
$V=s(X,Y)$ and a calibration set exchangeable with the test point, the prediction set formed from
the empirical $(1-\alpha)$ quantile of the calibration scores contains the truth with probability at
least $1-\alpha$~\cite{papadopoulos2002inductive,lei2018distribution}. The guarantee is marginal,
finite-sample, and free of modelling assumptions; its only structural requirement is
exchangeability, which is what operating-regime transfer destroys.

When exchangeability fails, Barber et al.~\cite{barber2023conformal} bound the resulting coverage
loss by the total-variation distances between the score vector and its versions with the test point
swapped against each calibration point; for independent data this reduces to pairwise
total-variation distances between the source and target score laws. This non-exchangeable bound is
the analytical backbone of the SCC certificate. Weighted (covariate-shift) conformal
prediction~\cite{tibshirani2019conformal} instead restores exact coverage using importance weights
$w(x)=\mathrm{d}P_T/\mathrm{d}P_S$; this is powerful but requires estimating the density ratio, and
hence representative target covariates. SCC differs in kind: it removes the shift physically, through
a dimensionless transformation, rather than reweighting statistically, and its certificate needs no
target data.

The physical transformation comes from \emph{dimensional similitude}. The Buckingham $\Pi$ theorem
reduces a dimensional relationship to dimensionless groups, and matching those groups enforces
dynamic similitude between systems. Recent work exploits this for transfer learning, training models
in dimensionless variables so they generalise across scales and operating
points~\cite{oppenheimer2023multiscale,therrien2024buckingham}, with exact policy transfer
guaranteed only under exact similitude~\cite{girard2024dimensionless}. These methods target point
accuracy and provide no calibrated uncertainty; SCC imports the same similitude principle into the
conformal calibration step to obtain a coverage guarantee.

The closest prior treatment of prognostic uncertainty is Javanmardi and
H\"ullermeier~\cite{javanmardi2023conformal}, who first conformalised RUL estimation on the C-MAPSS
benchmark using split conformal, conformalised quantile regression, and the non-exchangeable
variant. Where operating conditions vary, their remedy is to cluster them into a finite set of
\emph{known, discrete} modes and normalise within each; they note that this becomes inapplicable
when the modes are not known in advance or lack calibration data, and their non-exchangeable variant
weights calibration points by temporal recency rather than operating-regime similarity. SCC instead
handles \emph{continuous} operating-regime transfer through physical scaling, certifies coverage a
priori without target-regime data, and needs no discrete mode labels. Our concern is orthogonal to
point accuracy~\cite{lei2018machinery}: it is the validity of the interval when the operating regime
changes between calibration and deployment.
