\section{Case study: a controlled process-reliability testbed}\label{sec:design}
\subsection{Why a controlled testbed}\label{sec:why}
Demonstrating an a-priori certificate honestly requires data in which the governing physics actually
controls degradation, so that the similitude departure $\boldsymbol\psi$ is meaningful and the
certificate can be checked rather than asserted. We therefore use a stochastic catalyst-deactivation
simulation~\cite{levenspiel1999chemical,perry2008handbook}, a process-engineering reliability problem
in which a catalytic unit ages as its catalyst deactivates and reaches end of life when activity
falls below a threshold; the prognostic task is to predict the remaining life for catalyst-replacement
scheduling. Dynamic similitude is \emph{genuine} in the simulator but is never assumed by the
estimator, which sees only noisy activity signals and a nominal rate model. This separation permits a
non-circular test: we impose a graded, physically meaningful departure from similitude and check that
the certificate degrades exactly as~\eqref{eq:cert} predicts.

\subsection{Simulator}\label{sec:sim}
Deactivation follows first order, $\mathrm{d}a/\mathrm{d}t=-k_{\mathrm{eff}}(T)\,a$, with failure at
activity $a\le0.3$. The primary Arrhenius channel is $k_1=A_1e^{-E_1/RT}$ ($E_1=80$~kJ/mol); an
optional secondary channel $k_2=A_2e^{-E_2/RT}$ of weight $\eta$ provides the controlled departure
($E_2\neq E_1$). Unit-to-unit variability enters as a lognormal pre-exponential, and the activity
signal carries additive noise. At $\eta=0$ the dimensionless clock $\tau=t\,k_1(T)$ collapses every
temperature onto $a(\tau)=e^{-\tau}$: exact similitude, with the characteristic life $T_L=1/k_1(T)$
spanning $10.2\times$ across the three temperatures (600/650/700~K). The weight $\eta$ thus moves the
testbed continuously from exact similitude ($\eta=0$) into progressively stronger violations.

\subsection{Predictor, scores, and reliability metrics}\label{sec:metrics}
The predictor extrapolates remaining life from the observed activity using the nominal rate, and the
conformal layer covers the residual. Each metric is read in maintenance terms. \emph{Coverage}
(target $1-\alpha=0.90$) is the fraction of intervals that contain the true RUL, i.e.\ the realised
reliability of the maintenance decision; the \emph{coverage gap} $\max(0,(1-\alpha)-\text{coverage})$
is the shortfall against the promised reliability. \emph{Efficiency}, the relative interval back-off
$q_T/\overline{\text{RUL}}_T$, measures conservatism, i.e.\ the cost of unnecessarily early
replacement (smaller is more informative; a diverging value signals degenerate, uselessly wide
intervals). We also report the \emph{operational bound} $2(a+L\lVert\Delta\boldsymbol\psi\rVert)$ and
the \emph{diagnostic} verdict. Numbers are averaged over five seeds. Three acceptance criteria were
fixed before running: (1) naive conformal miscovers while SCC recovers at $\eta=0$; (2) the a-priori
bound, with $L$ fit on a subset of (pair, $\eta$) configurations, upper-bounds the gap on
\emph{held-out} configurations; and (3) the gap degrades gracefully and monotonically with $\eta$.
