\section{Formal coverage guarantee and proof}\label{app:proof}
This appendix gives the formal statement underlying Eq.~\eqref{eq:cert}: the dimensionless reduction,
the regularity hypotheses, the non-exchangeable bound used as a lemma, and the SCC certificate with
its proof and two-regime corollary.

\begin{definition}[Dimensionless reduction]\label{def:pi}
The Buckingham $\Pi$ theorem yields dimensionless groups, partitioned into (i) \emph{scale-setting}
groups, used to form a characteristic score scale $\sigma(\theta_c)>0$ such that the dimensionless
score $\tilde V=V/\sigma(\theta_c)$ has a condition-invariant law under exact similitude, and (ii) a
\emph{similitude-departure parameter} $\boldsymbol\psi(\theta_c)\in\mathbb R^m$ collecting residual
groups the scale does not absorb. $\boldsymbol\psi$ is constant across conditions when the
dimensionless model is complete. Let $\lawt c$ denote the law of $\tilde V$ under $\mathbb P_c$.
\end{definition}

\begin{assumption}[Lipschitz similitude departure]\label{ass:lip}
There exists $L<\infty$ with
$\dtv(\lawt c,\lawt{c'})\le L\lVert\boldsymbol\psi(\theta_c)-\boldsymbol\psi(\theta_{c'})\rVert$ for
all $c,c'$.
\end{assumption}
The exact-similitude boundary case
($\boldsymbol\psi\equiv\mathrm{const}\Rightarrow\lawt c=\lawt{c'}$, hypothesis H1) holds
\emph{irrespective of how far apart the scale-setting parameters are}; the global Lipschitz form
(hypothesis H2) is the regularity needed away from exact similitude. H1--H2 are physical hypotheses,
not theorems, and the diagnostic of Section~\ref{sec:diagnostic} tests them.

\begin{lemma}[\cite{barber2023conformal}]\label{lem:barber}
For split conformal with weights $w_i$ and pre-fitted scores, the coverage gap is at most
$(1+\sum_i w_i)^{-1}\sum_i w_i\,\dtv(R(Z),R(Z^i))$, where $R(Z)$ is the score vector and $R(Z^i)$
swaps the test point with calibration point $i$. For independent data,
$\dtv(R(Z),R(Z^i))\le 2\,\dtv(Z_i,Z_{n+1})$.
\end{lemma}

\begin{theorem}[SCC certificate]\label{thm:scc}
Under Assumption~\ref{ass:lip}, with calibration i.i.d.\ from $S$ and target
$(X_{n+1},Y_{n+1})\sim\mathbb P_T$ independent of calibration,
\[
\mathbb P\big(Y_{n+1}\in\mathcal C(X_{n+1})\big)\ge
1-\alpha-\tfrac{2n}{n+1}L\lVert\boldsymbol\psi(\theta_S)-\boldsymbol\psi(\theta_T)\rVert
\ge 1-\alpha-2L\lVert\boldsymbol\psi(\theta_S)-\boldsymbol\psi(\theta_T)\rVert.
\]
\end{theorem}
\begin{proof}
Coverage is the event $\{\tilde V_{n+1}\le\tilde q\}$ with $\tilde V_{n+1}\sim\lawt T$. Were the
dimensionless scores exchangeable (all $\lawt S$), split conformal would give coverage $\ge1-\alpha$.
Apply Lemma~\ref{lem:barber} with $w_i\equiv1$ (denominator $n+1$). The pre-fitted scores are
independent scalars; swapping calibration point $i$ with the test point exchanges
$\tilde V_i\sim\lawt S$ and $\tilde V_{n+1}\sim\lawt T$ while the other coordinates are unchanged. The
two joint laws are product measures differing in two independent coordinates, so by subadditivity of
total variation $\dtv(R(Z),R(Z^i))\le\dtv(\lawt S,\lawt T)+\dtv(\lawt T,\lawt S)=2\dtv(\lawt S,\lawt T)$.
Summing $n$ terms gives gap $\le\tfrac{2n}{n+1}\dtv(\lawt S,\lawt T)$, and Assumption~\ref{ass:lip}
bounds $\dtv(\lawt S,\lawt T)$ by $L\lVert\Delta\boldsymbol\psi\rVert$.
\end{proof}

\begin{corollary}[A-priori certificate, two regimes]\label{cor:apriori}
$\lVert\Delta\boldsymbol\psi\rVert$ is a physical quantity, not a function of target failure data.
\emph{(a)} Under complete similitude ($\boldsymbol\psi$ constant) the bound is $0$ and coverage is
$\ge1-\alpha$ for arbitrary differences in the scale-setting parameters, requiring only the target
scale $\sigma(\theta_T)$. \emph{(b)} Under incomplete similitude, coverage is certified down to
$1-\alpha-2L\lVert\Delta\boldsymbol\psi\rVert$ given a bound on the departure. Neither regime estimates
a density ratio, the property that distinguishes SCC from weighted and covariate-shift conformal.
\end{corollary}
