\section{Conclusion}
\label{sec:conclusion}

We presented an integrated soft-sensor framework organized around the production
failure modes that separate benchmarked models from trusted ones, and validated it
with a discipline matching its claims: one pipeline, one validation protocol, three
datasets chosen to span the assumption space --- including a negative control designed
to make the framework fail informatively. The components are individually simple; the
contribution is the composition and its accounting. Blocked cross-validation with a
parsimony rule makes selection reproducible where it was a lottery. An open-loop bias
update at the documented label delay removes the drift that caps every downstream
result. Adaptive conformal calibration on the corrected residuals delivers
regime-uniform coverage that a static construction cannot, provided the delayed-result bookkeeping pairs each laboratory value with the interval issued at its prediction. Functional
migration composes with the online layer to a 10.0$\times$ data-efficiency gain within a
process, while the limits of parameter-level transfer are stated rather than blurred.
And when the physics is absent and the point sensor fails, the calibration machinery
keeps telling the truth --- which we argue is the correct production stance: trust a
soft sensor by its interval width, not by the existence of its prediction. The
reference implementation, evidence artifacts with provenance stamps, and every figure
in this paper regenerate from single commands in the accompanying repository.
